\input jmsmac
\stretchpage
\blanktrue
\section* Getting started with GeomLab.

We have set up accounts on our lab computers to allow you to use
GeomLab during today's event.  The following instructions will guide
you through the process of logging in, opening a web browser, and
starting GeomLab.

\arabenum
\item
Type `\verb/demoNN/' and \verb/Return/ as the user name, where \verb/NN/
is the number written at the top of this sheet.
\item
Select \verb@Options/Session/Gnome 2.0 Desktop@.
\item
Type `\verb/open29apr/' and \verb/Return/ as the password.
\item
If a splash screen with zooming stars appears, click on \verb/OK/ to
proceed.
\item
A red dinosaur (representing the Mozilla web browser) appears in the
bar at the top of the screen.  Click once on it to launch the browser.
\item
At the right of the top border of the browser window are three little
buttons.  Click once on the middle button of the three to maximise the
window.
\item
Click in the address bar and type this address, followed by \verb/Return/:
\quotation
\verb@http://web.comlab.ox.ac.uk/geomlab@
\endquote
(You can use the same address to access GeomLab from school or home.)
\item
Click on the picture of interlocking fishes.
\item
Click on the Big Green Arrow.
\item
If a dialog box appears that offers to `open the default application',
click on \verb/OK/ to accept this.
\item
If a window appears that is labelled `Download Manager', click on the
rightmost of the three buttons (marked \verb/X/) to close it.
\item
If a window appears that offers to `trust a signed application', then
click on \verb/OK/ to accept it.
\endenum
When you have completed these steps, the GeomLab application should
appear, and you are ready to begin experimenting.

To use GeomLab from home or school, open a web browser, type the
address shown in Step~(7), and continue with the steps that follow.
Depending on the configuration of your computer, some of the dialog
boxes listed in later steps may appear.  If your computer does not
have Java installed, or your version of Java is too old to run
GeomLab, then you will be guided through the process of installing or
upgrading it; typically, this happens in a largely automatic way.

If you have difficulties, or want to comment on the website, do not
hesitate to get in touch with us by using the comment form that
appears on the site.  If you give an e-mail address, then we will
respond to you directly.
\end
